---
title: "Set User Role"
date: "`r Sys.Date()`"
output: 
  html_document: 
    df_print: paged
    code_folding: hide
params:
  viewer_group:
    input: text
    label: "Viewer Group"
    value: "role_viewer"
  publisher_group:
    input: text
    label: "Publisher Group"
    value: "role_publisher"
  admin_group:
    input: text
    label: "Administrator Group"
    value: "role_admin"
  run_report:
    input: select
    choices: [TRUE, FALSE]
    label: "Run Report?"
    value: false
---
```{r preflight_check, results='asis', include=TRUE}
if (
  nchar(Sys.getenv("RSTUDIO_CONNECT_SERVER")) == 0 ||
  nchar(Sys.getenv("RSTUDIO_CONNECT_API_KEY")) == 0
) {
  print(htmltools::h4("ERROR: Variables Not Defined"))
  print(htmltools::div(
    "The RSTUDIO_CONNECT_SERVER and RSTUDIO_CONNECT_API_KEY",
    "environment variables are required in order for this report",
    "to manage users. The API_KEY should represent an administrator",
    htmltools::br(),
    htmltools::br(),
    "Please define these variables",
    "and then re-run the report.",
    htmltools::br(),
    htmltools::br(),
    style = "max-width: 600px"
  ))
  knitr::knit_exit("Terminating the report early.")
}
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(blastula)
library(connectapi)
library(purrr)

# suppress email by default (enable if changes)
suppress_scheduled_email()

client <- connect()
```

This report will:

- get members in the group names specified by parameters
    - Viewer: "`r params$viewer_group`"
    - Publisher: "`r params$publisher_group`"
    - Admin: "`r params$admin_group`"
- map those users to the associated RStudio Connect user roles
- if a user is a member of multiple groups, they will get the greater of the roles

Are we going to run the report? (based on the parameter `run_report`, which
defaults to FALSE. In order to change it, either edit the YAML header or use the
`Knit with Parameters` option)

**`r ifelse(params$run_report, "YES", "NO")`**

```{r, echo=FALSE}
run_report <- as.logical(params$run_report)
if (!run_report) knitr::knit_exit("Terminating the report early.")
```

## Get the Connect Groups in Question

```{r get_groups}
# simple - only get 500 groups... no paging
all_groups <- client$groups(page_size = 500)

# find the entries we care about
viewer_group <- params$viewer_group
publisher_group <- params$publisher_group
admin_group <- params$admin_group
target_groups <- c(
  viewer_group, publisher_group, admin_group
  )

groups_list <- purrr::keep(all_groups$results, ~.x$name %in% target_groups)
groups_list <- purrr::set_names(
  groups_list, 
  purrr::map_chr(groups_list, ~ .x$name)
  )

groups_list
```

## Get the List of Members for those Groups

```{r get_group_membership}
viewer_members <- list();
publisher_members <- list();
admin_members <- list();

tryCatch({
viewer_guid <- groups_list[[viewer_group]]$guid
viewer_members <- client$group_members(viewer_guid)
}, error = function(e){print(e); message("Maybe viewer_group not found?")})

tryCatch({
publisher_guid <- groups_list[[publisher_group]]$guid
publisher_members <- client$group_members(publisher_guid)
}, error = function(e){print(e); message("Maybe publisher_group not found?")})

tryCatch({
admin_guid <- groups_list[[admin_group]]$guid
admin_members <- client$group_members(admin_guid)
}, error = function(e){print(e); message("Maybe admin_group not found?")})
```

## Find Users whose Role does not Match

> NOTE: Checking for users who are members of multiple groups

Conflicts are managed by preferring ADMIN > PUBLISHER > VIEWER. I.e. so a member
of the ADMIN group (`r admin_group`) who is also a member of the VIEWER group
(`r viewer_group`) will be assigned the role "administrator."

```{r find_group_membership_differences}
viewer_differences <- purrr::keep(
  viewer_members$results,
  ~ .x$user_role != "viewer" &&
    ! .x$guid %in% purrr::map_chr(publisher_members$results, function(x) x$guid) &&
    ! .x$guid %in% purrr::map_chr(admin_members$results, function(x) x$guid)
)

publisher_differences <- purrr::keep(
  publisher_members$results,
  ~ .x$user_role != "publisher" &&
    ! .x$guid %in% purrr::map_chr(admin_members$results, function(x) x$guid)
)

admin_differences <- purrr::keep(
  admin_members$results,
  ~ .x$user_role != "administrator"
)
```

```{r print_group_membership_differences}
simplify_function <- function(.list , .target) {
  list(
    current_role = .list$user_role,
    target_role = .target,
    username = .list$username,
    email = .list$email,
    user_guid = .list$guid
  )
}

exec_list <- c(
  purrr::map2(viewer_differences, "viewer", simplify_function),
  purrr::map2(publisher_differences, "publisher", simplify_function),
  purrr::map2(admin_differences, "administrator", simplify_function)
)

exec_df <- purrr::map_df(exec_list, identity)
exec_df
```

## Set Group Membership

```{r set_group_membership}
results <- purrr::pmap(
  list(
    guid = purrr::map_chr(exec_list, ~.x$user_guid),
    target_role = purrr::map_chr(exec_list, ~.x$target_role)
    ),
  function(guid, target_role, client) {
    client$users_update(user_guid = guid, user_role = target_role)
  },
  client = client
)

results
```

## Create an Email

If users have been changed, send an email.

- **`r nrow(exec_df)` users _to change_**
- **`r length(results)` users _changed_**

```{r send_email}
if (nrow(exec_df) > 0) {
  suppress_scheduled_email(FALSE)
  render_connect_email("set_user_role_email.Rmd") %>%
  attach_connect_email(
    subject = glue::glue("Changed {length(results)} User Role(s)"),
    attach_output = TRUE
  )
}
```
